Physics informed Multi-Modal Networks for Solar Wind modeling

### 2024-11-09 paper/main.tex
default

\section{Parker Neural Operator}

\subsection{Parker's Solar Wind model}
Parker's model of Solar wind establishes a radial outward propagation of the plasma through time:

\subsection{Neural Operators}

\subsection{Parker Kernel}

@@

\subsection{Theoretical model}
\subsubsection{Momentum Equation (Navier-Stokes)}
The momentum equation for an incompressible, electrically conducting fluid is given by:
\begin{equation}
\frac{\partial \mathbf{u}}{\partial t} + (\mathbf{u} \cdot \nabla) \mathbf{u} = -\nabla p + \nu \nabla^2 \mathbf{u} + \mathbf{J} \times \mathbf{B},
\end{equation}
where \( \mathbf{u} \) is the velocity field, \( p \) is the pressure, \( \nu \) is the kinematic viscosity, \( \mathbf{J} \) is the current density, and \( \mathbf{B} \) is the magnetic field.

>>>>

@@

\subsection{Theoretical model}
